A weakly structured stem for human origins in Africa

### 2022-01-09 paper.tex
add fig 2 and 3 drafts

\begin{figure}[ht]
\begin{center}
\makebox[\textwidth][c]{\includegraphics{figures/fig1.pdf}}
\caption{\textbf{Geography and genetic diversity within Africa}.
    \aprcomment{In the models presented below, we focus on the Nama, 
    Mende (MSL), Gumuz, and Oromo and Amhara.}
}
\label{fig:1}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\makebox[\textwidth][c]{} % \includegraphics{figures/fig2.png}}
\caption{\textbf{}.
    A placeholder - best fit model(s).
}
\label{fig:2}
\end{center}
\end{figure}

@@

@@

\begin{table}
    \centering
    \begin{tabular}{l|l|l}
        \toprule
        Parameter & Value & Something else \\
        \midrule
        x & y & z \\
        \bottomrule
    \end{tabular}
    \caption{caption}
    \label{tab:migration-rates}
\end{table}

@@

@@

\begin{figure}[ht]
\begin{center}
    \makebox[\textwidth][c]{} % \includegraphics{figures/fig3.pdf}}
\caption{\textbf{The third main figure}.
    A placeholder - validation (Relate and cSFS).
}
\label{fig:3}
\end{center}
\end{figure}

>>>>

\begin{figure}[ht!]
\begin{center}
\makebox[\textwidth][c]{\includegraphics{figures/fig1.pdf}}
\caption{\textbf{Geography and genetic diversity within Africa}.
    \aprcomment{In the models presented below, we focus on the Nama, 
    Mende (MSL), Gumuz, and Oromo and Amhara.}
}
\label{fig:1}
\end{center}
\end{figure}

@@

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/fig2}
    \caption{
        \textbf{Two best fit models with a weakly structured stem.}
        In both the the parameterizations of early population structure,
        continuous migration (A) and fragmentation with mergers (B), models
        that include ongoing migration between stem populations outperform
        those in which stem populations are isolated. Most populations are
        connected by continuous, reciprocal migration that are incidated by 
        double-headed arrows (labels matched to migration rates and divergence
        times in Table~\ref{tab:migration-rates}), and which lasts for the
        duration of concurrence of contemporaneous populations. The
        merger-with-stem-migration model (B) outperformed the
        continuous-migration model (A), $LL=-102,600$ vs $-115,500$,
        respectively, and both models provide a much better fit to diversity
        and LD statistics than a single-origin model of recent expansion.
    }
    \label{fig:2}
\end{figure}

@@

\begin{table}[t!]
    \centering
    \scriptsize
    \begin{tabular}{lllrrrr}
        \toprule
        \textbf{Likelihood} & \textbf{Label} & \textbf{Population Pair} &
            \textbf{Divergence} & \textbf{Migration rate} & \textbf{Migration} \\
        & & & 
            \textbf{Time (kya)} & \textbf{per generation} & \textbf{duration (ky)} \\
        \midrule
        \textbf{Continuous Model} & & & & & \\
        LL= -115,500 & a & Stem 1, Stem 2 & 1,163 & 6.43e-5 & 1,028 \\
        & b & Stem 2, Nama & NA & 5.82e-5 & 130 \\
        & c, d & Stem 2, Other Africans & NA & 3.10e-5, \textbf{1.64e-4} & 130, 55 \\
        & e, f & Nama, Other Africans* & 135 & 4.1e-5, 9.8e-6 & 135, 60 \\
        & g & Mende, East Africans & 60 & \textbf{2.14e-4} & 60 \\
        & h & East Africans, British & 50 & 4.17e-5 & 50 \\
        & i & Gumuz, Amhara/Oromo & 12 &\textbf{3.36e-4} & 12 \\
        \textbf{Merger Model} & & & & & \\
        LL= -102,600 & a & Stem 1, Stem 2 & 1,442 & \textbf{1.16e-4} & 963 \\
        & -- & Stem 1S, Stem 1E & 479 & 0 (fixed) & -- \\
        & b & Stem 2 to Nama & 119 & \textbf{0.71} & pulse \\
        & c & Stem 2 to Stem 1E & 98 & \textbf{0.50} & pulse \\
        & d & Stem 2 to Mende & 25 & \textbf{0.18} & pulse \\
        & e, f & Nama, Other Africans & 119 & 4.4e-5, 7.1e-6 & 119, 60 \\
        & g, & Mende, East Africans & 60 & \textbf{1.98e-4} & 60 \\
        & h & East Africans, British & 50 & 3.87e-5 & 50 \\
        & i & Gumuz, Amhara/Oromo &12 & \textbf{3.59e-4} & 12 \\
        \bottomrule
    \end{tabular}
    \caption{
        \textbf{Migration and divergence parameters from best fit models.}\\
        \aprcomment{Labels are keyed to Figure~\ref{fig:2}}
    }
    \label{tab:migration-rates}
\end{table}

@@

@@

\begin{figure}[t!]
    \centering
    \includegraphics{figures/fig3.pdf}
    \caption{
        \textbf{fig3}
    }
    \label{fig:3}
\end{figure}

@@
